---
title: "Predicting Audits"
author: "Jesse Vent"
output:
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Loading and Exploring Data

##Loading libraries required and reading the data into R

Loading R packages used besides base R.

```{r, message=FALSE, warning=FALSE}
library(Hmisc)
library(knitr)
library(ggplot2)
library(dplyr)
library(caret)
library(randomForest)
library(gridExtra)
library(ROCR)
library(corrplot)
library(tidyr)
library(rpart)
```

Below, I am reading the csv's as dataframes into R.

```{r}
train <- read.csv("audit_train.csv", stringsAsFactors = F, na.strings = c("NA", ""))
test <- read.csv("audit_test.csv", stringsAsFactors = F, na.strings = c("NA", ""))
```

##Data size and structure

Lets look at the structure first.

```{r}
str(train)
```

Below I am merging test and train, as this is required for data cleaning and feature engineering.

```{r}
test$Adjustment <- NA
test$Target <- NA
all <- rbind(train, test)

ggplot(data=all, aes(x=Education), fill=Target) +
    geom_bar(stat="count")
ggplot(data=all, aes(x=Employment)) +
    geom_bar(stat="count")
ggplot(data=all, aes(x=Marital)) +
    geom_bar(stat="count")
ggplot(data=all, aes(x=Occupation)) +
    geom_bar(stat="count")

```


##Completeness of the data

Lets see which variables contain missing values or NA's

```{r}
sapply(all, function(x) {sum(is.na(x))})
```
Lets replace the NA's for the categories with unknown as they haven't been provided. This could be a factor in itself.

```{r}
df <- all %>% replace_na(list("Employment" = "unknown", "Education" = "unknown", "Marital" = "unknown", "Occupation" = "unknown", "Accounts" = "unknown", "Gender" = "unknown"))
sapply(df, function(x) {sum(is.na(x))})
```
Now lets impute the NA variables in Age.
```{r}
summary(all$Age)
Agefit <- rpart(Age ~ Employment + Education + Marital + Occupation + Income + Gender + Deductions + Hours, data = df[!is.na(df$Age),], method = "anova")
df$Age[is.na(df$Age)] <- predict(Agefit, df[is.na(df$Age),])
sapply(df, function(x) {sum(is.na(x))})
```
Lets do the same for income, deductions and hours.
```{r}
Incomefit <- rpart(Income ~ Employment + Education + Marital + Occupation + Age + Gender + Deductions + Hours, data = df[!is.na(df$Income),], method = "anova")
df$Income[is.na(df$Income)] <- predict(Incomefit, df[is.na(df$Income),])

Deductionsfit <- rpart(Deductions ~ Employment + Education + Marital + Occupation + Income + Gender + Age + Hours, data = df[!is.na(df$Deductions),], method = "anova")
df$Deductions[is.na(df$Deductions)] <- predict(Deductionsfit, df[is.na(df$Deductions),])

Hoursfit <- rpart(Hours ~ Employment + Education + Marital + Occupation + Income + Gender + Deductions + Age, data = df[!is.na(df$Hours),], method = "anova")
df$Hours[is.na(df$Hours)] <- predict(Hoursfit, df[is.na(df$Hours),])
sapply(df, function(x) {sum(is.na(x))})
```

Adjustment relates to fraud amounts, lets just remove it for now and convert our category variables into factors.

```{r}
df$Adjustment <- NULL
df$Employment <-as.factor(df$Employment)
df$Education <- as.factor(df$Education)
df$Marital <- as.factor(df$Marital)
df$Occupation <- as.factor(df$Occupation)
df$Gender <- as.factor(df$Gender)
df$Accounts <- as.factor(df$Accounts)
```

###The Target Variable
Lets see how many people received a audit.

```{r, out.width="50%"}
ggplot(df[!is.na(df$Target),], aes(x = Target, fill = Target)) +
  geom_bar(stat='count') +
  labs(x = 'How many people needed an audit?') +
        geom_label(stat='count',aes(label=..count..), size=7) 
